\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic} % options: 'casual', 'classic', 'banking', 'oldstyle', 'fancy'
\moderncvcolor{blue}    % color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust the page margins
\usepackage[scale=0.9]{geometry}
\usepackage{needspace}

% Personal data
\firstname{Florian}
\familyname{Valade}
\title{Machine Learning Research Engineer}                     
\address{France}{}
\phone[mobile]{+33 6 17 57 19 12}
\email{florian\_val@outlook.fr}
\homepage{fvalade.fr}
\social[linkedin]{florian-valade}
\social[github]{FlorianVal}

\begin{document}
\makecvtitle

% PROFILE
\section{Profile}
Machine Learning Research Engineer specializing in efficient deep learning, large language models (LLMs), adaptive inference, and distributed training. Experienced in designing new architectures, running large-scale experiments, building multimodal systems, and optimizing GPU training infrastructure.

% HIGHLIGHTS
\section{Selected Research \& Engineering Highlights}
\cvlistitem{Trained and fine-tuned GPT-like LLMs (70M--1.3B parameters) on multi-GPU clusters (V100/A100) using FSDP, DDP, Accelerate, and custom distributed pipelines.}
\cvlistitem{Developed adaptive-inference methods (early exits, reject option, recursion) achieving significant FLOP reductions while preserving model accuracy.}
\cvlistitem{Built large-scale dataset pipelines: streaming loaders, deduplication, filtering, and curation.}
\cvlistitem{Designed compute-efficient Transformer variants and performed scaling-law analysis on loss--compute trade-offs.}
\cvlistitem{Built internal LLM tools for workflow automation.}
\cvlistitem{Managed GPU servers and research infrastructure; optimized throughput, training stability, and reproducibility.}

% EDUCATION
\section{Education}
\cventry{2022--Present}{PhD in Efficiency of Deep Learning Algorithms}{University Gustave Eiffel}{Paris, France}{}{}
\cventry{2021}{Master's Degree in Computer Science, Big Data and Machine Learning}{ECE Paris}{Paris, France}{}{}
\cventry{2015}{High School Diploma in Science}{L'Espérance High School}{Paris, France}{}{}

% PUBLICATIONS
\section{Publications}
\cvitem{2025}{\textbf{EERO: Early Exit with Reject Option} --- UAI 2025.
    \begin{itemize}
        \item Formalizes selective early exits using risk-coverage trade-offs.
        \item Respects strict compute budgets and improves the state-of-the-art speed/accuracy trade-off.
    \end{itemize}}
\cvitem{2024}{\textbf{Accelerating Large Language Model Inference with Self-Supervised Early Exits}.
    \begin{itemize}
        \item Introduces fine tuned early-exit extensions for LLMs using internal supervision signals.
        \item Enables FLOP-efficient inference with up to 50\% speedup.
        \item Achieves +66\% acceptance rate and 14x fewer wasted tokens compared to speculative decoding.
    \end{itemize}}

% EXPERIENCE
\needspace{6\baselineskip}
\section{Experience}

\cventry{2026--Current}{AI Research Engineer}{Fujitsu}{Paris, France}{}{
    \begin{itemize}
        \item Developing and adapting large language models for various applications.
    \end{itemize}}

\cventry{2022--2026}{PhD Candidate \& Research Engineer}{Fujitsu -- University Gustave Eiffel}{Paris, France}{}{
    \begin{itemize}
        \item Designed adaptive-inference architectures (early exits, recursion, selective prediction) for vision models and LLMs.
        \item Trained GPT-style models (70M--1.3B parameters) with FSDP, DDP, Accelerate, and distributed GPU clusters.
        \item Built large-scale data pipelines: filtering, deduplication, quality scoring, and multimodal curation.
        \item Conducted FLOP-efficient architecture research and compute scaling experiments.
        \item Built internal tooling for evaluation, model comparison, dataset validation, and visualization.
        \item Managed multi-GPU servers and training infrastructure.
        \item Taught Computer Vision and NLP to Master's students.
    \end{itemize}}

\cventry{2021--2022}{Data Scientist}{Fujitsu}{Paris, France}{}{
    \begin{itemize}
        \item Developed and deployed computer vision and deep learning systems for industry clients.
        \item Worked on multimodal applications combining vision, metadata, and text.
    \end{itemize}}

\cventry{2018--2021}{Apprentice Computer Vision Engineer}{Fujitsu -- ECE Paris}{Paris, France}{}{
    \begin{itemize}
        \item Applied deep learning to detection, segmentation, and embedded systems.
        \item Data collection, preprocessing, and pipeline engineering.
    \end{itemize}}

\cventry{2018}{Deep Learning Intern}{Fujitsu}{Paris, France}{}{
    \begin{itemize}
        \item Built demonstrators using deep learning for vision tasks.
    \end{itemize}}

% SKILLS
\section{Skills}
\cvitem{Machine Learning}{LLMs, Transformers, distributed training, multimodal AI, adaptive inference, model efficiency, calibration, data processing.}
\cvitem{Distributed Systems}{FSDP, DDP, Accelerate, DeepSpeed, Slurm, Docker, Kubernetes, multi-GPU clusters, profiling, monitoring.}
\cvitem{Programming}{Python, C, C\#, Java, SQL.}
\cvitem{Frameworks}{PyTorch, TensorFlow, JAX, MLX, HuggingFace ecosystem, W\&B, Git.}
\cvitem{Languages}{English (Fluent), French (Native), Spanish (Intermediate).}

% PROJECTS
\section{Projects}
\cvitem{2025}{\textbf{Recursive GPT}. Research project exploring scaling laws of recursive Transformers to reduce memory usage and improve FLOP efficiency; developed recursive-layer prototypes and analyzed compute scaling behaviors.}
\cvitem{2023}{\textbf{Adaptive Inference for LLMs}. Implemented early-exit heads and internal supervision layers on GPT-like models. Used Pythia and Phi models; fine-tuned intermediate heads; built evaluation tools for FLOP--loss trade-offs.}
\cvitem{2022}{\textbf{FreshDetect}. Real-time produce classification deployed using containerized microservices (PyTorch, Docker).}
\cvitem{2020}{\textbf{Handterpret}. Infrared-based hand-position detection system using embedded sensors.}
\cvitem{2017}{\textbf{AutoCradle}. Baby-cry detection triggering autonomous cradle rocking.}

\end{document}
